---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# solarEclipses

<!-- badges: start -->
<!-- badges: end -->

The goal of solarEclipses is to provide easy access to clean and structured data on solar eclipses for analysis and visualization. This R package includes detailed information on various types of solar eclipses, such as total and annular eclipses, along with their key attributes, including date, location, duration, and name. 

## Installation

You can install the development version of solarEclipses from [GitHub](https://github.com/) with:

``` r
# Install the development version from GitHub
devtools::install_github("Fengz924/solarEclipses")
```

## Example

This is a basic example which shows you how to load the dataset.

```{r example}
library(solarEclipses)
data("clean_eclipse_data")
```

The following code allow you to see the summary of the dataset:

```{r cars}
summary(clean_eclipse_data)
```


You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(clean_eclipse_data$duration)
```

